Xolotl: An Intuitive and Approachable Neuron \& Network Simulator in MATLAB

### 2018-07-11 paper/paper.tex
figs 1-6 modified; all fonts bigger

\begin{figure}[!htb]
	\centering
	\includegraphics[width=1.0\linewidth]{gfx/figure_network}
	\caption{Simulating a network of conductance-based model neurons. The diagram shows a three-compartment model of the pyloric network in the crustacean stomatogastric ganglion (Prinz \textit{et al.} 2004). Each neuron is modeled with a single compartment with 7-8 intrinsic conductances and 1-3 post-synaptic conductances. Synapses can be one of two types (Cholinergic (dashed lines) or Glutamatergic (solid lines)) and have different kinetics. The code snippet shows how neurons can be created, wired together using synapses, and how the model can be integrated to return voltages and intracellular calcium levels in every compartment, and the state of every synapse. (A-C) Simulated voltage trace of a model network for the three compartments obtained from this simulation. (D) Time series activation variable of the Glutamatergic synapse between PY and LP (red connection in diagram) shows how the synapse becomes active every time the PY neuron spikes.}
	\label{fig:figurenetwork}
\end{figure}

>>>>

\begin{figure}[!htb]
	\centering
	\includegraphics[width=1.0\linewidth]{gfx/figure_network}
	\caption{Simulating a network of conductance-based model neurons. (A) A three-compartment model of the pyloric network in the crustacean stomatogastric ganglion (cite Prinz \textit{et al.} 2004). Each neuron is modeled with a single compartment with 7-8 intrinsic conductances and 1-3 post-synaptic conductances. Synapses can be one of two types (Cholinergic (dashed lines) or Glutamatergic (solid lines)) and have different kinetics. (B) The code snippet shows how neurons can be created, wired together using synapses, and how the model can be integrated to return voltages and intracellular calcium levels in every compartment, and the state of every synapse. (C-E) Simulated voltage trace of a model network for the three compartments obtained from this simulation. (F) Time series activation variable of the Glutamatergic synapse between PY and LP (red connection in diagram) shows how the synapse becomes active every time the PY neuron spikes.}
	\label{fig:figurenetwork}
\end{figure}
